Functional Enrichment Tests: Intro and methods comparison

### 2023-06-21 DRAFT_Funct_Enrich.Rmd
cv annotation on FE

# Annotation

The following is a stepwise example or annotation of a gene set using Swiss-Prot such that Gene Ontology terms can be associated with each gene.

@@

@@

>>>>

# Navigating Annotation

The following is a stepwise example or annotation of a gene set using UniProt::Swiss-Prot (reviewed) such that Gene Ontology terms can be associated with each gene.

In this following chunk where the fasta file is downloaded the [release](https://www.uniprot.org/help/release-statistics) is noted and the file name is modified accordingly.

@@

A protein blast database is then made.

@@

In a majority of cases you will want to annotate a gene set to get gene ontology information. If you are creating your own genome or transcriptome it should be rather straightforward to know what file to annotate. If using a widely studied system where there are publically available resources, it is advisable to use those as this is the best way to facilitate integration of data sets. In this case study we will be considering the Eastern oyster, (_Crassostrea virginica_)

```{r engine='bash', eval=FALSE}
cd ../data

curl -O https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_protein.faa.gz

gunzip -k GCF_002022765.2_C_virginica-3.0_protein.faa.gz
```
